---
title: "HW4"
author: "Ming Zhong mz2692"
date: "10/20/2018"
output:
  pdf_document: default
  html_document:
    df_print: paged
---
```{r}
library("plyr")
debt <- read.csv("/Users/zhongming/Downloads/debt.csv", as.is = TRUE)
dim(debt)
head(debt)
```

#1.
```{r}
#Construct the function
mean.growth<-function(df){
  return(mean(df$growth))
}
#Using daply to get the average growth of different country
growth.country=daply(debt,.(Country),mean.growth)
#Print the value
round(c(growth.country["Australia"],growth.country["Netherlands"]),digits=2)
```

#2.
```{r}
#get the yearly average growth rate
growth.year=daply(debt,.(Year),mean.growth)
#print out the targeted yearly growth rate
round(c(growth.year["1972"],growth.year["1989"]),digits=2)
#plot the yearly growth rate
plot(names(growth.year),growth.year,xlab="Year",ylab="GDP Growth Rate(%)")
```

#3.
```{r}
#get the correlation between growth rate and ratio
round(cor(debt$growth,debt$ratio),digits = 4)
corr<-function(df){return(round(cor(df$growth,df$ratio),digits = 4))}
#compute correatlion for each country
corr.country=daply(debt,.(Country),corr)
#plot histogram
hist(breaks=10,corr.country,xlab="correlation coefficient",main="Country")
#compute correlation for each year
corr.year=daply(debt,.(Year),corr)
#plot histogram
hist(breaks=10,corr.year,xlab="correlation coefficient",main="Year")
#mean of correlation,which is around −0.1906
round(mean(corr.year),digits=5)
```

Are there any countries or years where the correlation goes against the general trend?\newline
```{r}
plot(corr.country,xlab="Country",ylab="correlation coefficients",xaxt = "n")
axis(side=1,at=1:20,labels=names(corr.country),las=2,cex.axis=0.5)
plot(x=as.numeric(names(corr.year)),y=corr.year,xlab="year",ylab="correlation coefficients")
```

Ans: It seems that Norway is goes against the general trend and the correlation around 1980 also goes against the trend.\newline

#4.
```{r}
#get the regreesino result
summary(lm(data=debt,growth~ratio))
debt=as.data.frame(debt)
#plot debt ratio against debt growth
plot(debt$ratio,debt$growth,xlab="debt ratio ",ylab="GDP growth")
abline(lm(data=debt,growth~ratio),col="red")
```

#5.
```{r}
#print out the name of the the 4 countries
country4=names(corr.country[corr.country<(-0.5)])
#plot 4 graphs in one figure
par(mfrow=c(2,2))
for (this.country in country4){
  country.dat<-subset(debt,Country==this.country)
  with(data=country.dat,plot(ratio,growth,main=this.country))
}
```

#6.
```{r}
#a.create new data frame
debt.France=subset(debt,Country=="France")
dim(debt.France)
year=debt.France$Year+1
#b.create new column
next.growth=rep(1,54)
for(i in 1:54){
  if(year[i] %in% debt.France$Year){
    next.growth[i]=debt.France[debt.France$Year==year[i],3]
  }
  else{
    next.growth[i]=NA
  }
}
debt.france=cbind(debt.France,next.growth)
#print out to test
round(debt.france[debt.france$Year==1971|debt.france$Year==1972,5],digits=3)
```

#7.
```{r}
#encapsulate question 6 into function
func<-function(df){
  y=df$Year+1
  next.growth=rep(NA,nrow(df))
  for(i in 1:nrow(df)){
    if(y[i] %in% df$Year){
      next.growth[i]=df[df$Year==y[i],3]
    }
    else{
      next.growth[i]=NA
    }
  }
  return(cbind(df,next.growth))
}
#get the data frame
df=ddply(debt,.(Country),func)
#doube check the France 2009 is NA
df[df$Country=="France"&df$Year==2009,"next.growth"]
```

#8.
```{r}
#plot next year’s GDP growth against this year’s debt ratio
plot(df$ratio,df$next.growth,xlab="next year GDP growth",ylab="Debt ratio")
#Linearly regress next year’s growth rate on the current year’s debt ratio
summary(lm(df$next.growth~df$ratio))
#d add the line to the plot
abline(lm(df$next.growth~df$ratio),col="red")
```

Ans:The regreesion result compared to the regression of the current year’s growth on the current year’s debt ratio is even worse. The R square of this result is smaller than the previous.\newline

#9.
```{r}
#plot of next year’s GDP growth against the current year’s GDP growth
with(data=df,plot(growth,next.growth))
#Linearly regress next year’s growth on this year’s growth
summary(lm(df$next.growth~df$growth))
#add the line to the plot
abline(lm(df$next.growth~df$growth),col="red")
```

Ans:The current growth is a better predictor.\newline
